Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
add another plot

We can also look at the

>>>>

We can also look at the effect of the network size.
Figure~\ref{fig:network} shows a comparison of the 10/10 boosting run
with the standard 13-isotope ``aprox13'' network and the reduced
7-isotope ``iso7'' network.  We see that the flame in the aprox13 case
is slightly more advanced and has a higher $\bar{A}$ than the iso7
case.  We see in the next section that these two networks give largely
the same flame speed.  The reduced network size saves a lot of memory
which will be important when we transition to 3-d simulations.

\begin{figure}[h]
\centering
\plotone{network_compare}
\caption{\label{fig:network} Mean molecular weight at 15~ms comparing a run with
  aprox13 vs a run with the iso7 network.}
\end{figure}

The final approximation to explore is our choice of rotation rate.
